The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-12 src/ms.tex
Update src/ms.tex
Co-authored-by: Nicholas Earl <contact@nicholasearl.me>

Several of the coordinated and affiliated packages described in
\cite{astropy:2018} have had substantial improvements. \texttt{astroquery}
\citep{astroquery} has added access to roughly a dozen new missions and data
services, including the James Webb Space Telescope (JWST) archive, and the
project has switched to a continuous release model: every time a change is
committed to the main development branch it is published on the Python Package
Index (PyPI) and available for installation. (However, formal releases are still
done a few times per year.) \texttt{photutils} \citep{photutils} released its
first stable version, indicating that the API will change less frequently, and
there have been several significant performance improvements. \texttt{ccdproc}
\citep{ccdproc}  released a new major version, bringing better performance to
some image combination operations. The \texttt{regions} package
\citep{pyregions}, for manipulating ds9-, CASA-, or FITS-style region definitions \citep{ds9},
added new ways to manipulate regions, introduced new region types, and obtained
expanded visualization and interactive region editing capabilities.
\texttt{reproject}'s \citep{reproject} major new feature is a function to align
and co-add images to create a mosaic; better support for parallelization was
also added. \texttt{specutils}, the package that defines containers for 1D and
2D spectra \citep{specutils},  had its first stable release and the addition
of classes to read JWST data. \texttt{stingray} has had a major performance
overhaul. The package \texttt{gammapy} \citep{gammapy} has major performance
improvements and has unified its API in preparation for its first stable
release.

>>>>

Several of the coordinated and affiliated packages described in
\cite{astropy:2018} have had substantial improvements. \texttt{astroquery}
\citep{astroquery} has added access to roughly a dozen new missions and data
services, including the James Webb Space Telescope (JWST) archive, and the
project has switched to a continuous release model: every time a change is
committed to the main development branch it is published on the Python Package
Index (PyPI) and available for installation. (However, formal releases are still
done a few times per year.) \texttt{photutils} \citep{photutils} released its
first stable version, indicating that the API will change less frequently, and
there have been several significant performance improvements. \texttt{ccdproc}
\citep{ccdproc}  released a new major version, bringing better performance to
some image combination operations. The \texttt{regions} package
\citep{pyregions}, for manipulating ds9-, CASA-, or FITS-style region definitions \citep{ds9},
added new ways to manipulate regions, introduced new region types, and obtained
expanded visualization and interactive region editing capabilities.
\texttt{reproject}'s \citep{reproject} major new feature is a function to align
and co-add images to create a mosaic; better support for parallelization was
also added. \texttt{specutils}, the package that defines containers for 1D and
2D spectra \citep{specutils},  had its first stable release and the addition
of classes to read JWST data. \texttt{stingray} has had a major performance
overhaul. The package \texttt{gammapy} \citep{gammapy} has had major performance
improvements and has unified its API in preparation for its first stable
release.
